---
title: "Questions to HW2"
author: "Nathan Bendriem"
date: "September 24, 2017"
output: 
  html_document: 
    keep_md: yes
---
### Homework 2:
Exploring the Gapminder dataset by using dplyr and ggplot2.  This page will contain the answers to the given questions as well as the codes and functions I used.

## Explore the Gapminder object:

# Is it a data.frame, a matrix, a vector, a list?
- It is a list
-typeof(gapminder)
# What's its class?
- a data frame table
-class(gapminder)
# How many variables/columns
-6
-ncol(gapminder)
# how many rows/observations
-1704
-nrow(gapminder)
# Can you get these facts about extent or size in more than one way?
-yes, you can also use the function dim(gapminder), and names(gapminder), length (gapminder) 
#what data type is each variable
- each variable is a tibble
- Country: factor
- continent: factor
- year: integer
- lifeExp: number
- pop: integer
- gdpPercap: number
-str(gapminder)

## Explore Individual Variables
- I will choose the categorical value "year" and quantitative category "lifeExp""
- Year has 12 integers (1952, 1957, 1962, 1967, 1977, 1987, 1992, 1997, 2002, 2007), and all occur 142 times
- table(gapminder$year)
- LifeExp has many more intergers, 
# What are the possible values of each variable?
- Years range from 1952 to 2007
- Life Expantancy ranges from 23.60 to 82.60 years
- summary(gapminder)
- unique(gapminder$year)
- unique(gapminder$lifeExp)

# What values are typical? Whats the spread, distribution,etc?
- Year: minimum is 1952, median is 1980, maximum is 2007.  The histogram shows that there is no year that is more popular then the others.  The average is 1989
- summary(gapminder$year)
- hist(gapminder$year)
- Life expectancy ranges from 23.60 to 82.60, with an average of 59.47 and a median of 60.71.  The histogram shows that the year class 70-75 is the most popular
- summary(gapminder$lifeExp)
- hist(gapminder$lifeExp)

##Explore Various Plot types
I will explore some various plots using the two variables Year and LifeExp

All of the graphs will be collated into a folder with the respective title of the graph.  I am having trouble having them remain within the md file.


# Scatterplot
```{r}
ggplot(gapminder, aes(x=year, y=lifeExp)) + geom_point(size= 1, colour= "red") + ggtitle("Gapminder dataset- LifeExp vs Year")

```

# Histogram
```{r}
ggplot(gapminder, aes(gapminder$lifeExp)) + geom_histogram(colour = "black", fill = "red", alpha= 0.33) + labs(x= "Life Expectancy", y= "Frequency") + ggtitle("Histogram of Life Expectancy")
```

## Use Filter, Select, and Piping

```{r}
ggplot(gapminder, aes(x= country, y= lifeExp)) + geom_boxplot(colour = "red",) + labs(x= "", y= "Life Expectancy") + ggtitle("Boxplot of Life Expectancy vs. Year")
```
This gives us too many inputs on the x axis (country) so we will do some filtering and focus only on North African Countries.

```{r}
NorthAfrica <- filter(gapminder, country== "Algeria" | country=="Tunisia" | country=="Egypt" | country=="Morocco" | country=="Libya" | country=="Sudan")
```
ggplot(NorthAfrica, aes(x= country, y= lifeExp)) + geom_boxplot(colour = "black", fill = "red", alpha= 0.33) + labs(x= "Country", y= "Life Expectancy") + ggtitle("Boxplot of Life Expectancy for North African Countries")

One more with Piping, focusing on Oceania and the years 1960-1980

```{r}
Oceania<- gapminder %>% filter(continent== "Oceania") %>% filter(year <= 1980, year >= 1960)
```

```{r}
ggplot(Oceania, aes(x= country, y=lifeExp)) + geom_boxplot(colour = "black", fill = "blue", alpha =0.33) +labs(x= "Country", y="Life Expectancy") + ggtitle("Boxplot of Life Expectancy for Oceania")
```






