---
title: "hw02"
author: "Nathan Bendriem"
date: "September 24, 2017"
output: 
  html_document: 
    keep_md: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

library(gapminder)
library(tidyverse)
str(gapminder)

class(gapminder)
summary(gapminder)
columns(gapminder)
ncol(gapminder)
nrow(gapminder)

Summary(gapminder)
```{r}
summary(gapminder)
```
mode(gapminder, year)
```{r}
hist(gapminder$year)
```
```{r}
summary(gapminder$year)
```
```{r}
summary(gapminder$lifeExp)
```
```{r}
hist(gapminder$lifeExp)
```
```{r}
ggplot(gapminder, aes(x=year, y=lifeExp)) + geom_point(), colour="red"
p1 <- ggplot(gapminder, aes(x=year, y=gdpPercap))
```

```{r}
head(unique(gapminder$year))
```
```{r}
```{r}
summary(gapminder$year)
```
nrow(gapminder$year)
tail(gapminder$year)
p1<- ggplot(gapminder, aes(x=year, y=gdpPercap))
p2<- 
```{r}
table(gapminder$year)
```
```{r}
table(gapminder$lifeExp)
```
```{r}
head(gapminder$lifeExp)
```
```{r}
tail(gapminder$lifeExp)
```
tail(unique(gapminder$lifeExp))```{r}
plot(p1)+ coluour="red"
```
p1 + geom(alpha=.66)
```{r}
p1 + geom_point(alpha=.66, colour="red")
```
```{r}
filter(gapminder, country=="France", year >1960, year <= 1980)
```
p3 <- filter(gapminder, country=="France", year >1960, year <=1980)

```{r}
plot(p3)
```
ggplot(p3)

```{r}
ggplot(p3, aes(x=year, y=pop))+ geom_point()
```
```{r}
```
hist(gapminder$country)
